---
title: "biz-record-linkage"
author: "brockwebb45@gmail.com"
date: "9/26/2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Synopsis
Generate a master set of businesses and two linkage sets (training/testing) that contain errors. The idea is that one will have to match the linkage file to the master record and correct/clean the data.

## Libraries

```{r}
#library()
```

## Data
FakeNameGenerator.com is good for addresses, not company names (too many duplicates). Could not find a sufficient "business name generator" to get things in bulk quantities... so we'll make our own with a few word lists...

```{r}
#Master list from FakeNameGenerator for addresses 
# A lot of duplicate company names to fix
masterF <- read.csv("./data/FakeNameGenerator.com_5467495b.csv",header=TRUE)

#Generate random company names
wlAnimals <- read.csv("./data/animals.csv")
wlBiztype <- read.csv("./data/biztypes.csv")
wlColors <- read.csv("./data/colors.csv")
wlFiction <- as.data.frame(read.csv("./data/fromfiction.csv", header=FALSE), stringsAsFactors=FALSE )
wlMath <- read.csv("./data/mathwords.csv")
wlScience <- read.csv("./data/sciencewords.csv")

#Using fiction list because, why not? Its nerd-tastic
#cnames <- as.data.frame(masterF$Name, stringsAsFactors=FALSE)


 cnames <- wlFiction


 
 
 
```





## Credits / References
fictional companies names: 
1) http://www.fakenamegenerator.com/order.php
2) https://myvocabulary.com/word-list/science-vocabulary/
3) http://www.english-for-students.com/Science-Words.html
4) https://github.com/hzlzh/Domain-Name-List/blob/master/Animal-words.txt
5) https://www.ncl.ucar.edu/Applications/Scripts/rgb.txt
6) http://brendoman.com/media/users/dan/finctional_companies.txt


