---
title: "biz-record-linkage"
author: "brockwebb45@gmail.com"
date: "9/26/2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Synopsis
Generate a master set of businesses and two linkage sets (training/testing) that contain errors. The idea is that one will have to match the linkage file to the master record and correct/clean the data.

## Libraries

```{r}
#library()
```

## Data
FakeNameGenerator.com is good for addresses, not company names (too many duplicates). Could not find a sufficient "business name generator" to get things in bulk quantities... so we'll make our own with a few word lists...

```{r}
#Master list from FakeNameGenerator for addresses 
# A lot of duplicate company names to fix
masterF <- read.csv("./data/FakeNameGenerator.com_5467495b.csv",header=TRUE)

#Generate random company names
wlAnimals <- read.csv("./data/animals.csv")
wlBiztype <- read.csv("./data/biztypes.csv")
wlColors <- read.csv("./data/colors.csv")
wlMath <- read.csv("./data/mathwords.csv")
wlScience <- read.csv("./data/sciencewords.csv")
```

```{r}

#Multiple picklists to randomly sample from 
#wlistpick <- data.frame(matrix(ncol=1, nrow = 4))
wlistpick <- data.frame(dfn=c("wlAnimals","wlColors","wlMath","wlScience"),stringsAsFactors = FALSE)

#extra rows and remove duplicates, need a 50k sample
tnames <- data.frame(matrix(ncol=1,nrow=100000))

for(i in 1:nrow(tnames)){
  
  # Number of words in business name
  roll <- sample(c(1,2,3),1)
  
  tn1<-NULL 
  
  for(j in 1:roll-1){
 
    x<-sample(c(1,2,3,4),1)
    
    if(x==1){
      tn <- as.character(sample(wlAnimals[[1]],1))
    }else if(x==2){
      tn <- as.character(sample(wlColors[[1]],1))
    }else if(x==3){
      tn <- as.character(sample(wlMath[[1]],1))
    }else{
      tn <- as.character(sample(wlScience[[1]],1))
    }
    tn1 <- paste(tn," ",tn1)    
  } 
    tn <- as.character(sample(wlBiztype[[1]],1))
    tn1 <- trimws(tn1,"r")
    tn1 <- paste(tn1,", ",tn,sep="")
    tnames[i,]<-tn1
  }
 
cnames <- unique(tnames)
    
tcnames <- as.data.frame(sample(cnames[,1],50000,replace=FALSE))
colnames(tcnames)<-c("Name")


masterF$Name <- tcnames$Name

write.csv(masterF,file="./data/masterCompanyFile.csv",row.names = FALSE)
 
```

# Adding errors to a copy of the master file, which will later be used for the training/test set

x <- c("this, is nice.", "nice, this is.")
gr <- gregexpr("[., ]", x)
regmatches(x,gr) <- lapply(lengths(gr), sample, x=c('|',':','@','*'))
x
```{r}
errorF <-masterF

#Drop the unique ID
errorF$BusinessGUID <- NULL

set.seed(123456)
for(i in 1:50000){ 

  for(j in 1:6){
  
    roll=sample(1:10000,1)
    
    if(roll>9300){
      errorF[i,j]<-"NA"
    }
  
  } #column lool  
} #Row loop 

write.csv(errorF,file="./data/errorF-NA.csv",row.names = FALSE)  
  
```



# Create the test and training sets
```{r}
errorF <- read.csv("./data/errorF-NA.csv", header = TRUE)

set.seed(10192017)
index <- sample(1:nrow(errorF),30000,replace=FALSE)
trainF <- errorF[index,] 
tF <- errorF[-index,]
index <- sample(1:nrow(tF),10000,replace=FALSE)
testF <- tF[index,]

write.csv(trainF,file="./trainingFile.csv",row.names = FALSE)
write.csv(testF,file="./testFile.csv",row.names = FALSE)
```

# Get working later

```{r}
 
#Function to substitute random typos, not working yet.
  for(m in 1:nchar(errorF[i,j])) 
      roll = sample(1:10000,1)
    
      if(l=="a"){x=c('q', 'w', 'z', 'x','')
      }else if(l=='b'){x=c('v', 'f', 'g', 'h', 'n','') 
      }else if(l=='c'){x=c('x', 's', 'd', 'f', 'v',''  )
      }else if(l=='d'){x=c('x', 's', 'w', 'e', 'r', 'f', 'v', 'c',''  )
      }else if(l=='e'){x=c('w', 's', 'd', 'f', 'r','' )
      }else if(l=='f'){x=c('c', 'd', 'e', 'r', 't', 'g', 'b', 'v','' )
      }else if(l=='g'){x=c('r', 'f', 'v', 't', 'b', 'y', 'h', 'n',''  )
      }else if(l=='h'){x=c( 'b', 'g', 't', 'y', 'u', 'j', 'm', 'n','' )
      }else if(l=='i'){x=c( 'u', 'j', 'k', 'l', 'o','' )
      }else if(l=='j'){x=c( 'n', 'h', 'y', 'u', 'i', 'k', 'm','' )
      }else if(l=='k'){x=c( 'u', 'j', 'm', 'l', 'o','' )
      }else if(l=='l'){x=c('p', 'o', 'i', 'k', 'm',''  )
      }else if(l=='m'){x=c( 'n', 'h', 'j', 'k', 'l','' )
      }else if(l=='n'){x=c('b', 'g', 'h', 'j', 'm',''  )
      }else if(l=='o'){x=c('i', 'k', 'l', 'p','' )
      }else if(l=='p'){x=c('o', 'l',''  )
      }else if(l=='q'){x=c('a','s','w','2','1','')
      }else if(l=='r'){x=c('e', 'd', 'f', 'g', 't',''  )
      }else if(l=='s'){x=c('q', 'w', 'e', 'z', 'x', 'c','' )    
      }else if(l=='t'){x=c('r', 'f', 'g', 'h', 'y','' ) 
      }else if(l=='u'){x=c('y', 'h', 'j', 'k', 'i','' ) 
      }else if(l=='v'){x=c('c', 'd', 'f', 'g', 'b','') 
      }else if(l=='w'){x=c('q', 'a', 's', 'd', 'e','' ) 
      }else if(l=='x'){x=c('z', 'a', 's', 'd', 'c','' ) 
      }else if(l=='y'){x=c('t', 'g', 'h', 'j', 'u','' ) 
      }else if(l=='z'){x=c('x', 's', 'a','' ) 
      }else if(l=='1'){x=c( '0','2','4','5') 
      }else if(l=='2'){x=c( '0','1','3','4','5','6') 
      }else if(l=='3'){x=c('2','4','5','6' ) 
      }else if(l=='4'){x=c('1','2','5','7','8' ) 
      }else if(l=='5'){x=c('1','2','3','4','6','7','8','9' ) 
      }else if(l=='6'){x=c('2','3','5','7','8','9' ) 
      }else if(l=='7'){x=c('4','5','6','8' ) 
      }else if(l=='8'){x=c('4','5','6','7','9' ) 
      }else if(l=='9'){x=c('0','5','6','8' ) 
      }else if(l=='0'){x=c( '1','2','9') 
      }else{}

    }#cell loop  

```



write.csv(masterF,file="./data/masterCompanyFile.csv",row.names = FALSE)


## Credits / References
fictional companies names: 
1) http://www.fakenamegenerator.com/order.php
2) https://myvocabulary.com/word-list/science-vocabulary/
3) http://www.english-for-students.com/Science-Words.html
4) https://github.com/hzlzh/Domain-Name-List/blob/master/Animal-words.txt
5) https://www.ncl.ucar.edu/Applications/Scripts/rgb.txt



